---
jupyter:
  jupytext:
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
      jupytext_version: 1.13.7
  kernelspec:
    display_name: R 4.0
    language: R
    name: ir40
---

```{r tags=c()}
library('ini')
library('tidyverse')
library('BayesFactor')
library('ggpubr')
```

## Introduction
Following the comment from the Reviewer:
> For TPJ and pSTS, a lateralized mask was used due to known asymmetries on the functional level. I wonder why the authors did not do the same for the FFA given its lateralization in the perception of faces in the left visual field / right hemisphere (e.g. Yovel et al. 2008).
> Yovel, G., Tambini, A., & Brandman, T. (2008). The asymmetry of the fusiform face area is a stable individual characteristic that underlies the left-visual-field superiority for faces. Neuropsychologia, 46(13), 3061-3068.

I would agree that there is reasonable basis to treat the FFA in a manner analogous to TPJ and pSTS, and use rFFA in the analysis (due to the reported right-hemispheric dominance). In this report I will assess the impact of FFA ROI laterality on the observed results and provide updated statistics.


## Method


I limited the current analysis to the OFL (US/noUS), because that's when participants actually process faces (also, bilateral FFA activations are pretty much zero during DE, but we report them in the paper for completeness).

Mecause I don't have an easy access to Matlab any more, I used a Python script (not yet on GitHub) to extract beta parameters for each subject and each condition (US, noUS) from right, left, and bilateral FFAs:

```{r}
config <- read.ini("config.ini")
df <- read_csv(file.path(config$extras$roi_output, 'ffa_betas.csv'), col_types=cols())
```

```{r}
head(df)
```

I'm converting the data frame to a tidy representation (1 row per observation):

```{r}
tidy_df <- df %>% 
    mutate(group = as.factor(group)) %>%
    pivot_longer(cols = where(is.numeric), names_to=c('side', 'condition'), names_sep='_',
                 values_to='contrast_estimate')
```

```{r}
head(tidy_df)
```

## Results


### Visual comparison (left vs right vs both)


Each subplot shows bars for left, right, and both FFAs; separatly for conditions (noUS / US, columns) and groups (friend / stranger, rows):

```{r}
tidy_df %>% ggbarplot(
    x = "side", y = "contrast_estimate", facet.by=c('group', 'condition'), add = c("mean_ci", "jitter"))
```

The same can be shown for US > noUS (calculated by subtracting the averaged parameters -- it would be more correct to rely on voxelwise subtraction ie. taking the relevant SPM beta file, but I'm approximating).

```{r}
tidy_df %>%
    pivot_wider(names_from=condition, values_from=contrast_estimate) %>%  # creates (us, no) columns, replacing condition and contrast estimate
    mutate(ur = us - no) %>%
    ggbarplot(x = "side", y = "ur", facet.by = "group", add = c("mean_ci", "jitter"))
```

### Numeric comparison: left vs right


From the two figures above it seems that we might have some laterality (R > L, as predicted) going on for stranger US. However, error bars suggest it's unlikely to be statistically significant:

```{r}
tidy_df %>% 
    filter(group=="stranger" & condition=="us" & side %in% c("left", "right")) %>%
    t.test(contrast_estimate ~ side, .)
```

```{r}
tidy_df %>% filter(group=="stranger" & condition=="us" & side %in% c("left", "right")) %>%
    ttestBF(formula = contrast_estimate ~ side, data = .) %>%
    (function(x) 1/x )(.)
```

Indeed, the right > left comparison (for stranger US) is not statistically significant (p > 0.05) though Bayes Factor indicates inconclusive evidence.


### Between-group comparison, bilateral FFA


In the paper we report t = 0.03, p=.98, BF=4.04 for the bilateral FFA. Let's confirm that we can replicate this for the current data frame (i.e. sanity check)

```{r}
frm = contrast_estimate ~ group
inv <- function(x) {1/x}
```

```{r}
tidy_df %>% head()
```

```{r}
tidy_df %>%
    filter(side=="both", condition=="us") %>%
    t.test(frm, .)
```

```{r}
tidy_df %>%
    filter(side=="both", condition=="us") %>%
    ttestBF(formula = frm, data = .) %>%
    inv()
```

### Between-group comparison, right FFA

```{r}
tidy_df %>%
    filter(side=="right", condition=="us") %>%
    t.test(frm, .)
```

```{r}
tidy_df %>%
    filter(side=="right", condition=="us") %>%
    ttestBF(formula = frm, data = .) %>%
    inv()
```

## Conclusion


- No significant (and arguably no meaningful) difference between R and L FFA
- For US (F>S), bilateral ROI, we reported t = 0.03, p = 0.98, BF = 4.04
- For US (F>S), right ROI, we would report t = -0.57, p = 0.57, BF = 3.52
- Our confidence in the null result decreases, but we still have moderate evidence of lack of effect.
- Suggest using rFFA and amending the results accordingly

```{r}

```
