---
title: Signature of pain
output:
  html_document:
    theme: spacelab
---

This analysis compares the multivariate expression of
"general vicarious pain pattern" from
[Zhou et al 2020](https://doi.org/10.7554/eLife.56929)
and "visually induced fear signature" from
[Zhou et al 2021](https://doi.org/10.1101/2020.11.23.394973)
between friend and stranger groups in observational fear learning.

The "signature expression" is defined as a dot product of Zhou et al's
published statistical map, and a given subject's contrast estimate
(SPM's con file) corresponding to US > noUS; see the
`signature_of_pain.py` script for implementation details.

```{r, message=FALSE}
library('ini')
library('tidyverse')
library('BayesFactor')
library('ggpubr')
```

## Inputs

Read paths from configuration:

```{r}
config <- read.ini("config.ini")
```

The statistical analysis relies on the outputs of Python processing:

```{r}
input_file <- file.path(config$extras$multivariate_output, 'pattern_expression.csv')
pattern_expression  <- read_csv(input_file, col_types=cols())
```

Group assignment can be read from the participant information table:

```{r}
subject_info_file <- file.path(config$extras$osf_data, "Behavioral", "table.tsv")
groups <- read_tsv(subject_info_file, col_types=cols()) %>%
    filter(role=="OBS") %>%
    select(c("label", "group"))
```

Assembling into one tibble for analysis:

```{r}
df <- left_join(pattern_expression, groups, by="label") %>%
    relocate("group", .after="label")
head(df)
```

## Statistics

```{r}
df %>%
    pivot_longer(
        cols=starts_with("dot_"),
        names_to="signature",
        values_to="expression") %>%
    mutate(signature = fct_relevel(signature, "dot_pain", "dot_fear")) %>%
    ggboxplot(
        x="group",
        y="expression",
        facet.by="signature",
        add="jitter",
    )
```

### Pain

Frequentist t-test:

```{r}
t.test(dot_pain ~ group, df)
```

Bayesian t-test:

```{r}
ttestBF(formula = dot_pain ~ group, data = df)
```

### Fear

Frequentist t-test:

```{r}
t.test(dot_fear ~ group, df)
```

Bayesian t-test:

```{r}
ttestBF(formula = dot_fear ~ group, data = df)
```
