---
output:
  html_document:
    theme: spacelab
---

# Contingency knowledge

```{r, message=FALSE}
library('tidyverse')
library('eulerr')
library('ggpubr')
library('ini')
```

This analysis formally compares contingency knowledge between friend and strangers group,
using a contingency table / chi-squared test.

```{r}
config <- read.ini("../config.ini")

tab_file <- file.path(config$DEFAULT$QUESTIONNAIRE_DIR, 'table.tsv')
df <- read_tsv(tab_file, col_types=cols())
figures_dir <- 'figures'  # store figures next to code
```

## Overall analysis (friend vs stranger group)
### Create a contingency table

```{r}
x <- df %>%
    filter(role=="OBS") %>%
    select(c("label", "group", "CONT_contingency")) %>%
    drop_na()

ct <- x %>%
    count(group, CONT_contingency) %>%
    pivot_wider(names_from = CONT_contingency, values_from = n) %>%
    column_to_rownames("group") %>%
    rename(aware = YES, nonaware = NO) %>%
    relocate(aware, .before = nonaware)
	
ct
```

### Perform a chi-squared test
Use the basic formulation, without Yates' continuity correction.

```{r}
chisq.test(ct, correct=FALSE)
```

## Additional analysis, with by-demonstrator matching

### Subset and pivot
We can now treat the demonstrator id as the id column, and for each demonstrator obtain outcome from friend & stranger:

```{r}
x <- df %>%
    filter(role=="OBS") %>%
    select(c("group", "demonstrator_id", "CONT_contingency")) %>%
    pivot_wider(names_from = group, values_from = "CONT_contingency") %>%
    drop_na() %>%                      # remove those not seen by strangers
    mutate(
        stranger = stranger == "YES",  # converts to boolean
        friend = friend == "YES",      # converts to boolean
    )
```

### Count demonstrators correctly identified by both / either / none
```{r}
outcomes <- x %>%
    count(friend, stranger) %>%
    mutate(
        outcome = case_when(
            friend & stranger ~ "Both",
            friend & !stranger ~ "Friend only",
            !friend & stranger ~ "Stranger only",
            TRUE ~ "Neither",
            )
        ) %>%
    select(outcome, n)
outcomes
```

### Portray that as an Euler plot
The data may be too simple for that, but I couldn't resist.

```{r}
fit <- x %>%
    select(c("friend", "stranger")) %>%
    euler()

p <- plot(fit, quantities=TRUE, legend=TRUE)

if(!dir.exists(figures_dir)) {dir.create(figures_dir)}
ggexport(p, filename = file.path(figures_dir, "euler.png"))
p
```
