---
output:
  html_document:
    theme: spacelab
---

# Motion outliers

In the fMRI analysis, "motion outliers" flagged by fMRIprep were added
as regressors. A decision was made to exclude subjects for whom more
than 25 % of volumes were flagged as such (leading to exclusion of one
subject). The numbers of outliers were calculated in
`spm/complete/prepare.m`. This notebook reports on the average /
median number of motion outlier regressors used.

```{r, message = FALSE}
library("tidyverse")
library("rstatix")
library("ini")
```

Load the output produced by `spm/complete/prepare.m`

```{r}
config <- read.ini("../config.ini")
tbl_path <- file.path(config$SPM$ROOT, "complete", "other",
                      "motion_outliers.csv")
df <- read_csv(tbl_path, col_types = cols())
df
```

Matching other analyses, select fitting data. Use 90 & 45 as approximate cut-offs for both groups, as there are no edge cases (there were 362/380 and 184 volumes, so exact cut-offs are 91/95 and 46).

```{r}
df %>%
    filter(motion_ofl < 90 & motion_de < 45) %>%
    get_summary_stats(show=c("min", "max", "median", "mean"))
```

