---
jupyter:
  jupytext:
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
      jupytext_version: 1.11.1
  kernelspec:
    display_name: R
    language: R
    name: ir
output: 
  html_document:
    theme: spacelab
---

# Questionnaires

This analysis compares the results of STAI and SWE questionnaires between friend and stranger groups.

```{r, message=FALSE}
library('tidyverse')
library('afex')
library('emmeans')
library('BayesFactor')
library('ggpubr')
library('ini')
```


We are working with the following files:
```{r}
config <- read.ini("../config.ini")
tab_file <- file.path(config$DEFAULT$QUESTIONNAIRE_DIR, 'table.tsv')
```

The analysis is based on the observers included in the MRI sample:

```{r}
df <- read_tsv(tab_file, col_types=cols())
```

```{r}
df <- df %>%
    filter(role == "OBS") %>%             # observers only
    filter(CONT_contingency == "YES") %>% # contingency knowing only
    filter(label != "Nagery")             # included in MRI only
```

## State anxiety

Data preparation & wide-format export for JASP:

```{r}
state_anxiety <- df %>% 
    select(c("label", "group", starts_with("STAI_state"))) %>%
    pivot_longer(starts_with("STAI_state"), names_to = "measurement") %>%
    mutate(
        measurement = recode_factor(measurement, 
                                    "STAI_state1_total" = "before", 
                                    "STAI_state2_total" = "after"),
        group = as_factor(group)
        )
```

```{r}
# temporarily write wide-format for jasp
if (!dir.exists("tmp_outputs")) { dir.create("tmp_outputs") }
df %>% 
    select(c("label", "group", starts_with("STAI_state"))) %>%
    write_tsv('tmp_outputs/state_anxiety_ctg.tsv')
```

### Classical ANOVA

```{r tags=c()}
a_state_anxiety <- aov_ez(
    id = "label", 
    dv = "value",
    data = state_anxiety,
    between = "group",
    within = "measurement"
)

a_state_anxiety
```

### Bayesian anova
Performed separately in JASP. Couldn't figure out how to do it in BayesFactor.


## STAI Trait

```{r}
trait_anxiety <- df %>%
    select(c("label", "group", "STAI_trait_total"))
```

```{r}
t.test(STAI_trait_total ~ group, trait_anxiety)
ttestBF(data = trait_anxiety, formula = STAI_trait_total ~ group)
```

## Skala Wrażliwości Empatycznej

```{r}
empathy <- df %>% 
    select(c("label", "group", starts_with("SWE")))
```

### empathic concern

```{r}
t.test(SWE_empathic_concern ~ group, empathy)
ttestBF(formula = SWE_empathic_concern ~ group, data = empathy)
```

### personal distress

```{r}
t.test(SWE_personal_distress ~ group, empathy)
ttestBF(formula = SWE_personal_distress ~ group, data = empathy)
```

### perspective taking

```{r}
t.test(SWE_perspective_taking ~ group, empathy)
ttestBF(formula = SWE_perspective_taking ~ group, data = empathy)
```

# Appendix: additional plots & stats

## State Anxiety

Paired plot:

```{r}
state_anxiety_plot <- ggpaired(state_anxiety, x = "measurement", y = "value", id = "label", facet.by = "group")

if(!dir.exists("figures")) { dir.create("figures") }
ggexport(state_anxiety_plot, filename = 'figures/state_anxiety.png')
state_anxiety_plot
```

Simple contrasts (within measurement or group) with uncorrected p-values:

```{r}
rbind(
    pairs(emmeans(a_state_anxiety, ~group|measurement)),
    pairs(emmeans(a_state_anxiety, ~measurement|group)),
    adjust = "none"
)
```

## "Trait" questionnaires combined

```{r}
traits_plot <- df %>% 
    select(c("label", "group", starts_with("SWE"), "STAI_trait_total")) %>%
    pivot_longer(starts_with(c("SWE", "STAI")), names_to = "scale.name") %>%
    mutate(
        scale.name = str_replace_all(scale.name, "_", " "),
    ) %>%
    ggboxplot(x = "group", y = "value", facet.by = "scale.name", add = "jitter", nrow=1)
ggexport(traits_plot, filename = "figures/stai_trait_and_swe.png")
traits_plot
```
