---
output:
  html_document:
    theme: spacelab
---

# Skin conductance

This analysis contains statistical tests for the skin conductance response amplitudes produced by PsPM.

```{r, message=FALSE}
library('tidyverse')
library('ggpubr')
library('afex')
library('emmeans')
library('ini')
```

```{r}
config <- read.ini("../config.ini")

pspm_root <- config$PSPM$ROOT
tmp_outputs <- "tmp_outputs"
fig_dir <- "figures"

if(!dir.exists(tmp_outputs)) {dir.create(tmp_outputs)}
if(!dir.exists(fig_dir)) {dir.create(fig_dir)}
```

The tables contain only contingency-aware subjects, so there is no need to filter based on that

```{r}
df_ofl <- read_tsv(file.path(pspm_root, 'all_ofl.tsv'), col_types = cols())
df_de <- read_tsv(file.path(pspm_root, 'all_de.tsv'), col_types = cols())
```

Display the number of subjects per group

```{r}
df_ofl %>%
    group_by(group) %>%
    summarise( count = n_distinct(subject) )
```

## OFL


Average trials within subjects. Note that PsPM treats all trials equally during estimation, so each kind of trial contains two responses: flexible response #1 (CS) and fixed response #1 (US, be it present or absent). We are interested in the latter.

```{r}
ws_avg_ofl <- df_ofl %>%
    filter(trialinfo == 'Fixed response # 1') %>%  # US response
    group_by(subject, stimulus, group) %>%
    summarise(m_amplitude = mean(amplitude, na.rm=TRUE)) %>%
    ungroup()
```

With fixed responses selected, we want to compare CS+ reinforced to CS+ nonreinforced trials (ie. US to noUS).

```{r}
ofl_anova_data <- ws_avg_ofl %>%
    filter(str_starts(stimulus, "CS plus")) %>%  # be it reinforced or not
    mutate(across(where(is_character), as_factor)) # explicit conversion to factor
```

Run the classical anova and view the results

```{r}
anova_ofl <- aov_ez(
    id = "subject",
    dv = "m_amplitude",
    data = ofl_anova_data,
    between = "group",
    within = "stimulus",
)
```

```{r}
anova_ofl
```

```{r}
pairs(emmeans(anova_ofl, ~ stimulus), reverse = TRUE)
```

Note: the above call to emmeans produces results equivalent to `t.test(m_amplitude ~ stimulus, ofl_anova_data, paired = TRUE)`

```{r}
plot_ofl <- afex_plot(
    object = anova_ofl,
    x = "stimulus",
    data_plot = FALSE,
    error = "within",
    factor_levels=list(
        stimulus=c(CS.plus.reinforced = 'US', CS.plus.nonreinforced = 'noUS')),
    ) + labs(y = "amplitude (arb. unit)") + ggpubr::theme_pubr()

plot_ofl
```

Note: the plot presents the main effect of the stimulus. Error bars (`error = "within`) represent 95 % (default) confidence intervals based on within-subject standard errors calculated using the Cosineau-Morey-O'Brien method. Details can be found in the [documentation]() for `afex_plot`, including the following passage:

> In the case of designs involving repeated-measures factors the usual confidence intervals or standard errors (i.e., model-based confidence intervals or intervals based on the standard error of the mean) cannot be used to gauge significant differences as this requires knowledge about the correlation between measures. One popular alternative in the psychological literature are intervals based on within-subjects standard errors/confidence intervals (e.g., Cousineau & O'Brien, 2014). These attempt to control for the correlation across individuals and thereby allow judging differences between repeated-measures condition.

General comments on error bars can also be found in the [Afex plot documentation](https://cran.r-project.org/web/packages/afex/vignettes/afex_plot_introduction.html#error-bars-for-mixed-models).

## DE


Again, start by averaging trials within subject. This time we are looking at the "flexible" response, ie. the response to the CS; during direct-expression this is the only response in a trial.

```{r}
ws_avg_de <- df_de %>%
    group_by(subject, group, stimulus) %>%
    summarise(m_amplitude = mean(amplitude, na.rm = TRUE)) %>%
    ungroup()
```

For DE there are two trial types (CS+ & CS-) so no need to filter, just convert text to factors explicitly.

```{r}
de_anova_data <- ws_avg_de %>%
    mutate(across(where(is_character), as_factor))
```

Run the anova and display the results

```{r}
anova_de <- aov_ez(
    data = de_anova_data,
    id = "subject",
    dv = "m_amplitude",
    within = "stimulus",
    between = "group"
    )
```

```{r}
anova_de
```

```{r}
summary(anova_de)
```

```{r}
pairs(emmeans(anova_de, ~ stimulus), reverse = TRUE)
```

As a side note, even though there is no effect of group or interaction, only one group shows "significant" effects in post-hoc pairwise comparisons:

```{r}
pairs(emmeans(anova_de, ~ stimulus | group), reverse = TRUE)
```

```{r}
plot_de <- afex_plot(
    object = anova_de,
    x = "stimulus",
    data_plot = FALSE,
    error = "within",
    factor_levels = list(
        stimulus = c(CS.plus = "CS+", CS.minus = "CS-"))
    ) +
    labs(y = "amplitude (arb. unit)") +
    ggpubr::theme_pubr()


plot_de
```

## Data export


Create a wide format table expected by JASP (it is easier to run bayesian anovas there). Stimulus names are different for the two tasks, so the tibbles can be joined without any further changes.

```{r}
ofl_jasp_data <- ofl_anova_data %>%
    pivot_wider(names_from = stimulus, values_from = m_amplitude)
de_jasp_data <- de_anova_data %>% 
    pivot_wider(names_from = stimulus, values_from = m_amplitude)

jasp_data <- full_join(ofl_jasp_data, de_jasp_data,
                       by = c("subject", "group"))

write_tsv(jasp_data, file.path(tmp_outputs, "skin_conductance.tsv"))
```


## Combined plot

```{r}
target_ppi = 300
scr_plot <- ggarrange(plot_ofl, plot_de, common.legend = TRUE, labels = "AUTO")
ggexport(
    scr_plot,
    filename = file.path(fig_dir, "scr_anova.png"),
    width = 3.94 * target_ppi,
    height = 3.54 * target_ppi,
    res = target_ppi,
    pointsize = 10
    )
scr_plot
```
